\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-30 paper.qmd
Updated fitted values section

The prediction approach involves performing the K-nearest neighbors (KNN) algorithm for an unsupervised classification problem. First, the nearest \pD{} model point is identified for a given new \pD{} point. Then, the corresponding \kD{} centroid mapping for the identified \pD{} model point is determined. Finally, the coordinates of this \kD{} centroid are used as the predicted \kD{} embedding for the new \pD{} data point. .

@@

To assess how well our method captures and represents the underlying structure of the \pD{} data, residuals are important. Residuals are computed by taking the squared \pD{} Euclidean distance, $\sum_{i = 1}^{n}\sum_{j = 1}^{p} (x_{ij} - C^{(p)}_{hx_ij})^2$. Additionally, Mean Squared Error (MSE), $\frac{1}{n}\sum_{i = 1}^{n}\sum_{j = 1}^{p}(x_{ij} - C^{(p)}_{hx_ij})^2$, is computed based on residuals.

>>>>

<!-- The prediction approach involves performing the K-nearest neighbors (KNN) algorithm for an unsupervised classification problem. First, the nearest \pD{} model point is identified for a given new \pD{} point. Then, the corresponding \kD{} centroid mapping for the identified \pD{} model point is determined. Finally, the coordinates of this \kD{} centroid are used as the predicted \kD{} embedding for the new \pD{} data point. . -->

We define the function $z: \mathbb{R}^{n\times p} \rightarrow \mathbb{R}^{m\times p}$.

For the $i^{th}$ point, $z(i) = \arg\min_{j = 1, \dots, b} \sqrt{\sum_{v=1}^{P}(x_{iv} - C^{(2)}_{jv})^2}$, and assign it to $H_h = \{i| z(i) = h\}$. Then, the fitted values for $i$ are defined as $C_{h}^{(2)} = (c_{h1}, c_{h2})$.

@@

To assess how well our method captures and represents the underlying structure of the \pD{} data, residuals are important. Residuals are computed by taking the squared \pD{} Euclidean distance, $\sum_{i = 1}^{n}\sum_{j = 1}^{p} (x_{ij} - C^{(p)}_{hj})^2$. Additionally, Mean Squared Error (MSE), $\frac{1}{n}\sum_{i = 1}^{n}\sum_{j = 1}^{p}(x_{ij} - C^{(p)}_{hj})^2$, is computed based on residuals.

### 2024-05-30 paper.tex
Updated fitted values section

The prediction approach involves performing the K-nearest neighbors
(KNN) algorithm for an unsupervised classification problem. First, the
nearest \pD{} model point is identified for a given new \pD{} point.
Then, the corresponding \kD{} centroid mapping for the identified \pD{}
model point is determined. Finally, the coordinates of this \kD{}
centroid are used as the predicted \kD{} embedding for the new \pD{}
data point. .

@@

To assess how well our method captures and represents the underlying
structure of the \pD{} data, residuals are important. Residuals are
computed by taking the squared \pD{} Euclidean distance,
\(\sum_{i = 1}^{n}\sum_{j = 1}^{p} (x_{ij} - C^{(p)}_{hx_ij})^2\).
Additionally, Mean Squared Error (MSE),
\(\frac{1}{n}\sum_{i = 1}^{n}\sum_{j = 1}^{p}(x_{ij} - C^{(p)}_{hx_ij})^2\),
is computed based on residuals.

>>>>

We define the function
\(z: \mathbb{R}^{n\times p} \rightarrow \mathbb{R}^{m\times p}\).

For the \(i^{th}\) point,
\(z(i) = \arg\min_{j = 1, \dots, b} \sqrt{\sum_{v=1}^{P}(x_{iv} - C^{(2)}_{jv})^2}\),
and assign it to \(H_h = \{i| z(i) = h\}\). Then, the fitted values for
\(i\) are defined as \(C_{h}^{(2)} = (c_{h1}, c_{h2})\).

@@

To assess how well our method captures and represents the underlying
structure of the \pD{} data, residuals are important. Residuals are
computed by taking the squared \pD{} Euclidean distance,
\(\sum_{i = 1}^{n}\sum_{j = 1}^{p} (x_{ij} - C^{(p)}_{hj})^2\).
Additionally, Mean Squared Error (MSE),
\(\frac{1}{n}\sum_{i = 1}^{n}\sum_{j = 1}^{p}(x_{ij} - C^{(p)}_{hj})^2\),
is computed based on residuals.
